---
title: "Sujeet ITC stock Time Series Analysis"
output: html_notebook
---

This is our second assignment for RSTM subject. 

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r}
# I am running the whole test in ITC stock
# # Required Packages
packages = c('quantmod','car','forecast','tseries','FinTS', 'rugarch','utf8','ggplot2')
# # Install all Packages with Dependencies on first run
# install.packages(packages, dependencies = TRUE)
# # Load all Packages
lapply(packages, require, character.only = TRUE)
# 0.1. Fetch Single Stock/Index Data
getSymbols(Symbols = 'ITC.NS', 
           src = 'yahoo', 
           from = as.Date('2018-01-01'), 
           to = as.Date('2023-12-31'),
           periodicity = 'daily')

stock_price = na.omit(ITC.NS$ITC.NS.Adjusted) 
class(stock_price) # Time-Series Object

stock_ret = na.omit(diff(log(stock_price))) # Stock Returns
plot(stock_price)
plot(stock_ret)#this is stock return of ITC
```
```{r}
# Augmented Dickey-Fuller (ADF) Test for Stationarity with Stock Data

adf_test_stk_price = adf.test(stock_price); adf_test_stk_price  #  Non-Stationary

adf_test_stk_ret = adf.test(stock_ret); adf_test_stk_ret # Stationary
```
```{r}
# Ljung-Box Test for Autocorrelation - Stock Data
# ***********************************************

lb_test_stk_ret = Box.test(stock_ret); lb_test_stk_ret # Inference : Stock Difference (Stationary) Time-Series is Autocorrelated

# Autocorrelation Function (ACF) | Partial Autocorrelation Function (PACF)
# *****************************************************************************

acf(stock_price) # ACF of Stock Price
pacf(stock_price) # PACF of Stock Price

acf(stock_ret) # ACF of Stock Return (Stationary) Series
pacf(stock_ret) # PACF of Stock Return (Stationary) Series
```
```{r}
# Auto ARIMA
arma_pq_stk_ret = auto.arima(stock_ret); arma_pq_stk_ret
arma_pq_stk = auto.arima(stock_price); arma_pq_stk
```
```{r}
# Ljung-Box Test for Autocorrelation - Model Residuals
# ****************************************************
lb_test_arma_pq_stk_ret = Box.test(arma_pq_stk_ret$residuals); lb_test_arma_pq_stk_ret

# Forecasting with ARIMA Models
# ************************************
# jj_ds_f11 = predict(arma11, n.ahead = 40)
# plot(jj_ds_f11)
# lines(jj_ds_f11$pred, col = 'blue')
# lines(jj_ds_f11$pred + 2 * jj_ds_f11$se, col = 'red')
# lines(jj_ds_f11$pred - 2 * jj_ds_f11$se, col = 'red')

stock_ret_fpq = forecast(arma_pq_stk_ret, h = 40)
plot(stock_ret_fpq)

stock_fpq = forecast(arma_pq_stk, h = 40)
plot(stock_fpq)
```
```{r}
# Test for Volatility Clustering or Heteroskedasticity: Box Test 
stk_ret_sq = arma_pq_stk_ret$residuals^2 # Return Variance (Since Mean Returns is approx. 0)
plot(stk_ret_sq)
stk_ret_sq_box_test = Box.test(stk_ret_sq, lag = 10) # H0: Return Variance Series is Not Serially Correlated
stk_ret_sq_box_test # Inference : Return Variance Series is Heteroskedastic (Has Volatility Clustering)

# Test for Volatility Clustering or Heteroskedasticity: ARCH Test
stk_ret_arch_test = ArchTest(arma_pq_stk_ret$residuals, lags = 10) # H0: No ARCH Effects
stk_ret_arch_test # Inference : Return Series is Heteroskedastic (Has Volatility Clustering)
```
```{r}
# GARCH Model
garch_model1 = ugarchspec(variance.model = list(model = 'sGARCH', garchOrder = c(1,1)), mean.model = list(armaOrder = c(0,0), include.mean = TRUE))
nse_ret_garch1 = ugarchfit(garch_model1, data = arma_pq_stk_ret$residuals); nse_ret_garch1

garch_model2 = ugarchspec(variance.model = list(model = 'sGARCH', garchOrder = c(1,1)), mean.model = list(armaOrder = c(4,5), include.mean = FALSE))
nse_ret_garch2 = ugarchfit(garch_model2, data = arma_pq_stk_ret$residuals); nse_ret_garch2

# Test for Volatility Clustering or Heteroskedasticity: ARCH Test
gar_resd = residuals(nse_ret_garch2)^2
stk_ret_arch_test1 = ArchTest(gar_resd, lags = 1) # H0: No ARCH Effects
stk_ret_arch_test1 # Inference : Return Series is Heteroskedastic (Has Volatility Clustering)
```
```{r}
garch_modelf = ugarchspec(variance.model = list(model = 'sGARCH', garchOrder = c(1,1)), mean.model = list(armaOrder = c(4,5), include.mean = FALSE))
stk_ret_garch = ugarchfit(garch_modelf, data = stock_ret); stk_ret_garch
```
```{r}
# GARCH Forecast
stk_ret_garch_forecast1 = ugarchforecast(stk_ret_garch, n.ahead = 50); stk_ret_garch_forecast1
plot(stk_ret_garch_forecast1)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

